\documentclass{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[left=25mm,right=25mm, top=30mm, bottom=30mm]{geometry}
\hypersetup{colorlinks=true,urlcolor=blue}
\begin{document}
\title{Literature}
{\Large Useful materials without any particular order or grouping:}
\begin{enumerate}
\item Dennis Ritchie,Brian Kernighan "The C Programming Language" (Second Edition) - this is classic.
\item \href{http://www.open-std.org/jtc1/sc22/wg14/www/docs/n1548.pdf}{The latest C11 standard document} - the most authoritative source of information about C language, rather hard to read and understand though.
\item \href{http://www.open-std.org/jtc1/sc22/wg14/www/C99RationaleV5.10.pdf}{"Rationale for International Standard Programming Languages C."} - provides a lot of information about the language itself and reasons for many decisions in language design.
\item \href{http://people.ece.cornell.edu/land/courses/ece4760/cbook1_1.pdf}{Derek M. Jones, "The New C Standard, An Economic and Cultural Commentary."} - gigantic monograph, each line from C standard is thoroughly commented.
\item \href{http://en.cppreference.com/w/c}{"C reference"} - provides easy access to documentation regarding various C/CPP language aspects including standard library reference.
\item \href{https://www.securecoding.cert.org/confluence/display/c/SEI+CERT+C+Coding+Standard}{SEI CERT C Coding Standard} - very useful resource devoted to secure coding in C; as most of security issues in C programs stem from misusage and misunderstanding of language constructs this is a very useful resource about how NOT to code in C.
\item \href{https://www.akkadia.org/drepper/cpumemory.pdf}{What Every Programmer Should Know About Memory} - a classical work from Ulrich Drepper about computer memory (memory access, CPU caches, memory hardware, virtual memory, NUMA and so on); rather technical work but contains a lot of useful and interesting information.
\item "Expert C Programming: Deep C Secrets" By Peter van der Linden - a lot of nice tricks and a many of interesting C aspects; dated back to 1994 and interestingly enough is still actual for modern programming.
\item "Linkers and loaders" by John R. Levine - good overview of how binary files are created and then loaded to memory, covers different aspects of static and dynamic linking on different platforms, examine ELF format in details, provides historical overview of many choices and decisions in modern linkers and loaders.

\end{enumerate}
\end{document}
