\input{../head.tex}

\title{Development tools}

\begin{document}
\frame{\titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{make}
\justifying Make is a build automation tool that automatically builds executable programs and 
libraries from source code by reading files called Makefiles which specify how to 
derive the target program. \newline

Useful options:
    \begin{itemize}
        \item \textbf{-d} to print debugging information in addition to normal processing
        \item \textbf{-jN} to specify the number of jobs to run simultaneously
        \item \textbf{-p} to print data base (rules and variable values) that results from reading the makefiles
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{binutils}
The GNU Binutils are a collection of binary tools. The main ones are \textbf{ld} (the GNU linker) and \textbf{as} (the GNU assembler).
Additional useful tools from it which often used:

    \begin{itemize}
        \item \textbf{addr2line} - Converts addresses into filenames and line numbers.
        \item \textbf{ar} - A utility for archives manipulations.
        \item \textbf{c++filt} - Filter to demangle encoded C++ symbols.
        \item \textbf{gprof} - Displays profiling information.
        \item \textbf{nm} - Lists symbols from object files.
        \item \textbf{objcopy} - Copies and translates object files.
        \item \textbf{objdump} - Displays information from object files.
        \item \textbf{readelf} - Displays information from ELF object files.
        \item \textbf{size} - Lists the section sizes of an object or archive file.
        \item \textbf{strings} - Lists printable strings from files.
        \item \textbf{strip} - Discards symbols.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{valgrind}
\justifying Valgrind is an instrumentation framework for building dynamic analysis tools.
There are Valgrind tools that can automatically detect many memory management and threading bugs,
and profile your programs in detail. You can also use Valgrind to build new tools. \newline

Popular tools:
    \begin{itemize}
        \item \textbf{memcheck} detects memory-management problems, targeted mainly at C and C++, detects invalid memory access, use of un-initialized memory, memory leaks, double frees, bad frees, mis-uses of memory functions
        \item \textbf{cachegrind} a cache profiling tool
        \item \textbf{callgrind} a call profiling tool
        \item \textbf{hellgrind} a thread debugger which finds data races in multithreaded programs
    \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
